\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

\definecolor{sectioncolor}{RGB}{0,51,102}

\titleformat{\section}
  {\large\bfseries\color{sectioncolor}}
  {}{0em}{}[\titlerule]

\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

% ================= HEADER =================
\begin{center}
    {\LARGE \textbf{ENOKA EMBIENNE YVAN MAEL}}\\
    \vspace{2mm}
    \textit{Infrastructure, Cloud \& Network Engineer | IT Project Manager}\\
    \vspace{2mm}
    Douala, Cameroon \\
    \href{mailto:maelenokaembienne@outlook.fr}{maelenokaembienne@outlook.fr} | +237 695 00 35 67
\end{center}

% ================= SUMMARY =================
\section*{Professional Summary}
Dynamic and detail-oriented IT professional with nearly four years of experience in system and network administration, cloud infrastructure, and IT project coordination. Strong background in hybrid cloud environments, security, automation, and DevOps practices. Passionate about continuous improvement, infrastructure optimization, and delivering reliable IT solutions aligned with business objectives.

% ================= EXPERIENCE =================
\section*{Professional Experience}

\textbf{Willis Towers Watson – Douala, Cameroon} \\
\textit{Network and Partnership Support Engineer} \hfill \textbf{Nov 2024 – Present}
\begin{itemize}
    \item Managed and developed strategic partnerships, ensuring coordination and resolution of technical and administrative issues.
    \item Conducted statistical and decision analysis through data collection, modeling, and visualization.
    \item Developed reporting and monitoring tools to support operational and management decision-making.
\end{itemize}

\textbf{ACTIVA Assurances Group – Douala (Cameroon) / Abidjan (Ivory Coast)} \\
\textit{Project Management \& Infrastructure Engineer} \hfill \textbf{Aug 2022 – Jun 2024}
\begin{itemize}
    \item Designed and deployed network infrastructures (MDT, WSD) and identity management solutions (Active Directory, Azure IAM).
    \item Administered Fortigate firewalls, FortiCloud Manager, and implemented endpoint protection with BitDefender.
    \item Configured Alcatel L2/L3 switches, VLAN segmentation, and network security policies.
    \item Coordinated the deployment of the Hyperion system in Abidjan as part of a cross-country IT project.
    \item Implemented monitoring solutions (Zabbix) and optimized performance in hybrid cloud environments.
\end{itemize}

\textbf{FACE AUX RISQUES PROFESSIONNELS SA – Douala, Cameroon} \\
\textit{Infrastructure Manager} \hfill \textbf{Jan 2022 – Aug 2022}
\begin{itemize}
    \item Optimized network infrastructure through LAN redesign, structured cabling, and VPN client-to-site deployment.
    \item Deployed and administered systems including Active Directory, WampServer, and ERP (Dolibarr).
    \item Implemented containerized environments using Docker and continuous deployment pipelines.
    \item Installed and managed physical access control systems (badge-based access).
\end{itemize}

% ================= SKILLS =================
\section*{Technical Skills}

\textbf{Cloud Platforms:} Microsoft Azure (Azure AD, Virtual Machines, Functions, Monitor, Security Center) \\
\textbf{CI/CD \& DevOps:} Azure DevOps, GitHub Actions, Jenkins \\
\textbf{Automation \& Scripting:} PowerShell, Python, Bash, Ansible \\
\textbf{Containerization \& Virtualization:} Docker, Kubernetes (AKS), Hyper-V, KVM \\
\textbf{Monitoring \& Logging:} Azure Monitor, Zabbix, ELK Stack \\
\textbf{Networking \& Security:} VPN, Firewalls, Load Balancers, RBAC, IAM, DNS, DHCP, FortiCloud, BitDefender

% ================= PROJECTS =================
\section*{Key Projects}

\textbf{DevOps Architecture for Continuous Improvement}
\begin{itemize}
    \item Designed and deployed a DevOps architecture enabling CI/CD, automated testing, and scalable containerized services.
    \item Implemented unified service communication to improve system reliability and operational efficiency.
\end{itemize}

\textbf{Active Directory Automation}
\begin{itemize}
    \item Developed PowerShell scripts to automate user provisioning and directory management tasks.
\end{itemize}

% ================= EDUCATION =================
\section*{Education}

\textbf{Computer Engineering Degree} – Institut UCAC-ICAM \\
\textit{Sep 2019 – Jul 2024}

\textbf{Microsoft Azure Administrator (AZ-104)} – Orange Digital Center \\
\textit{Sep 2023 – Oct 2023}

% ================= CERTIFICATIONS =================
\section*{Certifications}

\begin{itemize}
    \item VMware Certifications
    \item Microsoft Azure Administrator (AZ-104)
    \item Oracle Cloud Infrastructure 2023 Certified Foundations Associate
    \item Cisco Network Technician Career Path
    \item Scrum Fundamentals Certified (SFC)
    \item DevOps on AWS
    \item Fortinet NSE 1, NSE 2, NSE 3 – Network Security Associate
\end{itemize}

% ================= LANGUAGES =================
\section*{Languages}

\begin{itemize}
    \item French: C2 (Native/Fluent)
    \item English: B2 (Professional Working Proficiency)
\end{itemize}

% ================= ADDITIONAL =================
\section*{Additional Information}

\begin{itemize}
    \item Strong organizational, communication, and project coordination skills
    \item Driver’s License: Category B
    \item Interests: Sports (Handball, Football, Basketball, Swimming), Music (Piano, Guitar), Artificial Intelligence
\end{itemize}

\end{document}
